Reviving stochasticity: SMBH-binary eccentricity is inherently random

### 2023-06-06 papers/paper-eccentricity/paper-eccentricity.tex
- minor changes to discussion

Conversely, in the real universe, variation in the impact parameter of a similar magnitude to the presented simulations, but as a consequence of different processes, is expected due to the lack of system reproducibility.
As with many physical systems, random variations in the system state demand the use of statistics to ascertain a most probable configuration or outcome. 
\drafting{Discussion about Sgr $A^*$ proper motion and oscillation scales? Or better example?}.

>>>>

Conversely, in the real universe, variation in the impact parameter of a similar magnitude to the presented simulations, but as a consequence of different processes, is expected due to the lack of system reproducibility.
As with many physical systems, random variations in the system state demand the use of statistics to ascertain a most probable configuration or outcome. 
Work by \citet{batcheldor2010} has suggested that the SMBH in M87 may be displaced from the galactic photo-centre by $\sim7\,\mathrm{pc}$ due to jet acceleration or gravitational recoil kicks. 
Assuming these processes are at play in other galaxies (particularly elliptical galaxies constructed through major mergers), deviations of a few parsecs of the SMBH from the host galaxy photo-centre are expected and would influence the impact parameter two merging SMBHs would experience.
